Events

### 2024-09-03 notebooks/events/e11.qmd
feat: encounter 9

> E11, C6, Q8, Q9 23–27 February, 2022. PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihe- lion with the Earth–Sun–STEREO-A angle '40◦ and the Earth– Sun–SO angle decreasing from '15◦ to 0◦ on 7 March, 2022, with SO at 0.5 AU. There will be clear opportunities here for cross calibration of magnetic ﬁeld measurements, as well as a true stereoscopic reconstruction of the solar corona crossed by PSP, with opportunities for all the PSP–SO objectives.

>>>>

> E11, C6, Q8, Q9 23–27 February, 2022. PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihelion with the Earth–Sun–STEREO-A angle '40◦ and the Earth– Sun–SO angle decreasing from '15◦ to 0◦ on 7 March, 2022, with SO at 0.5 AU. There will be clear opportunities here for cross calibration of magnetic ﬁeld measurements, as well as a true stereoscopic reconstruction of the solar corona crossed by PSP, with opportunities for all the PSP–SO objectives.
